---
title: "fjds;ajfksaj"
author: "Varun Gupta"
date: "May 31, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(data.table)
require(boot)
dataf <- read.csv("nbt.3154-S3.csv")
celltypes <- read.csv("celltypes.csv")[, "x"]
dataf[,"type"] <- celltypes
```

Wilcoxon analysis:
```{r}
locs <- data.frame(gene = character(), onetwo = numeric(), twothree = numeric(), threefourg = numeric(), threefourgf = numeric(), fourgfourgf = numeric(), stringsAsFactors = FALSE)
pvals <- data.frame(gene = character(), onetwo = numeric(), twothree = numeric(), threefourg = numeric(), threefourgf = numeric(), fourgfourgf = numeric(), stringsAsFactors = FALSE)
lows <- data.frame(gene = character(), onetwo = numeric(), twothree = numeric(), threefourg = numeric(), threefourgf = numeric(), fourgfourgf = numeric(), stringsAsFactors = FALSE)
highs <- data.frame(gene = character(), onetwo = numeric(), twothree = numeric(), threefourg = numeric(), threefourgf = numeric(), fourgfourgf = numeric(), stringsAsFactors = FALSE)

for (i in 2:47) {
  gene <- colnames(data)[i]
  locs[i-1, "gene"] <- gene
  pvals[i-1, "gene"] <- gene
  lows[i-1, "gene"] <- gene
  highs[i-1, "gene"] <- gene
  
  onetwo <- wilcox.test(dataf[dataf$type == "PS", gene], dataf[dataf$type == "NP", gene], conf.int = TRUE)
  locs[i-1, "onetwo"] <- onetwo$estimate
  pvals[i-1, "onetwo"] <- onetwo$p.value
  lows[i-1, "onetwo"] <- onetwo$conf.int[1]
  highs[i-1, "onetwo"] <- onetwo$conf.int[2]
  
  twothree <- wilcox.test(dataf[dataf$type == "NP", gene], dataf[dataf$type == "HF", gene], conf.int = TRUE)
  locs[i-1, "twothree"] <- twothree$estimate
  pvals[i-1, "twothree"] <- twothree$p.value
  lows[i-1, "twothree"] <- twothree$conf.int[1]
  highs[i-1, "twothree"] <- twothree$conf.int[2]
  
  threefourg <- wilcox.test(dataf[dataf$type == "HF", gene], dataf[dataf$type == "4G", gene], conf.int = TRUE)
  locs[i-1, "threefourg"] <- threefourg$estimate
  pvals[i-1, "threefourg"] <- threefourg$p.value
  lows[i-1, "threefourg"] <- threefourg$conf.int[1]
  highs[i-1, "threefourg"] <- threefourg$conf.int[2]
  
  threefourgf <- wilcox.test(dataf[dataf$type == "HF", gene], dataf[dataf$type == "4GF", gene], conf.int = TRUE)
  locs[i-1, "threefourgf"] <- threefourgf$estimate
  pvals[i-1, "threefourgf"] <- threefourgf$p.value
  lows[i-1, "threefourgf"] <- threefourgf$conf.int[1]
  highs[i-1, "threefourgf"] <- threefourgf$conf.int[2]
  
  fourgfourgf <- wilcox.test(dataf[dataf$type == "4G", gene], dataf[dataf$type == "4GF", gene], conf.int = TRUE)
  locs[i-1, "fourgfourgf"] <- fourgfourgf$estimate
  pvals[i-1, "fourgfourgf"] <- fourgfourgf$p.value
  lows[i-1, "fourgfourgf"] <- fourgfourgf$conf.int[1]
  highs[i-1, "fourgfourgf"] <- fourgfourgf$conf.int[2]
}

rownames(locs) <- locs[, "gene"]
locs <- locs[,-1]
rownames(pvals) <- pvals[, "gene"]
pvals <- pvals[,-1]
rownames(lows) <- lows[, "gene"]
lows <- lows[,-1]
rownames(highs) <- highs[, "gene"]
highs <- highs[,-1]

png("~/Downloads/locs.png")
par(mar = rep(0, 4))
pheatmap(locs, cluster_row = FALSE, cluster_col = FALSE, color = heat.colors(12), labels_col = c("PS-NP", "NP-HF", "HF-4G", "HF-4GF", "4G-4GF"))
dev.off()

png("~/Downloads/pvals.png")
par(mar = rep(0, 4))
pheatmap(pvals, cluster_row = FALSE, cluster_col = FALSE, color = heat.colors(1), breaks = c(0, 0.05/230, 1), labels_col = c("PS-NP", "NP-HF", "HF-4G", "HF-4GF", "4G-4GF"))
dev.off()
```

HF --> 4GF is continuing course, whereas HF --> 4G requires drastic increase in expression of endothelial genes and drastic decrease in expression of erythroid genes
```{r}
quantile(locs[,"threefourgf"])
quantile(locs[,"threefourg"])
```

```{r}
locs[,c("threefourg", "threefourgf")] > 1
```
Increases:
Endothelial: Cdh5, Egfl7, Erg, Ets1, Ets2, Etv2, Etv6, Fli1, Hhex, HoxB4, Kr, Kit, Meis1, Notch1, Pecam1, Sox17, Sox7, Tbx20
Erythroid: FoxH1, Fox04, Runx1
```{r}
locs[,c("threefourg", "threefourgf")] < -1


locs[c("FoxH1", "FoxO4", "Runx1"),c("threefourg", "threefourgf")]
```
Decreases:
Endothelial: Gata1, Gfi1b, HbbbH1, Ikaros, Itga2b, Myb, Nfe2, Runx1
Erythroid: none

Correlation matrix:
```{r}
M <- cor(dataf[,2:47])

png("~/Downloads/CorrelationMatrix.png")
par(mar = rep(0, 4))
M <- cor(dataf[,2:47])
corrplot(M, method = "circle")
dev.off()

```

Bootstrapped correlations:
```{r}
cf <- function(d, i){
	d2 <- d[i,]
	return(cor(d2[,1], d2[,2]))
}

bootcorr1 <- boot(dataf[,c("Gfi1b", "Gata1")], cf, R=500)
mean(bootcorr1$t)
bootcorr1
cor.test(dataf$Gfi1b, dataf$Gata1)
bootcorr2 <- boot(dataf[,c("HoxB4", "Sox7")], cf, R=500)
mean(bootcorr2$t)
bootcorr2
cor.test(dataf$HoxB4, dataf$Sox7)
bootcorr3 <- boot(dataf[,c("Notch1", "Ets1")], cf, R=500)
mean(bootcorr3$t)
bootcorr3
cor.test(dataf$Notch1, dataf$Ets1)
bootcorr4 <- boot(dataf[,c("Erg", "Myb")], cf, R=500)
mean(bootcorr4$t)
bootcorr4
cor.test(dataf$Erg, dataf$Myb)
```
We must adjust the p-values for the multiple comparison problem. However, the first three correlations are such that their p-values are essentially 0, so no adjustment is necessary. The fourth correlation estimate is insignificant under the traditional cut-off level of 0.05, so no adjustment is necessary. 